Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

% (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.

\begin{comment}
\medskip
By definition the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but is also a direct fuction of viscocity ratio (\ie VR). If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate. On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate. Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil. Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates. The method that has been described in this paper as well as the simulations performed have a number of distinct advantages; (1.) The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and because the geological characteristic and parameters can be easily introduced without the need of upscaling while, (2.) computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate (unstructured grid in space and time) and manage using fewer grid cells. The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.

>>>>

% (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.
Through

\begin{comment}\medskip
By definition the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but is also a direct fuction of viscocity ratio (\ie VR). If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate. On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate. Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil. Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates. The method that has been described in this paper as well as the simulations performed have a number of distinct advantages; (1.) The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and because the geological characteristic and parameters can be easily introduced without the need of upscaling while, (2.) computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate (unstructured grid in space and time) and manage using fewer grid cells. The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.
